Veasel meets FOX: an ensemble approach to entity linking based on vector similarity

### 2015-07-10 paper.tex
minor updates

We compare our approach to state-of-the-art tools such as FOX\cite{foxdemo} and DBpedia spotlight\cite{spotlight}, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset. Further, we show that Veasel beats state-of-the-art named entity linking approaches in terms of speed.

@@

The input data for {\acronym} is a regular piece of text, for example a newspaper article, in which entity-representing sequences of tokens (\emph{fragments}) are already identified (we use the Stanford NER \cite{ner}). For a given fragment, the algorithm's task is to determine the matching real-world entity. It does so by picking the most likely entity from a set of entity candidates, e.g. specified in a knowledge base, in our case DBpedia.

@@

The semantic neighborhood signature for an entity is computed in a similar way as Babelfy \cite{babelfy} does, except that instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base we use a graph of interlinked Wikipedia pages, where each page is a vertex and each link between pages is an edge. The idea is to identify for each resource all other resources it is closely related to. This is a two step process. First, the edges are assigned weights so that edges in denser parts of the graph become more important. The weight of an edge $\mathrm{weight}(v, v')$ is the number of directed triangles (directed cycles of length 3) it appears in:
$$\mathrm{weight}(v, v') := |\{(v, v', v'') : (v, v'), (v', v''), (v'', v) \in E\}| + 1$$

@@

We compute a measure similar to the \emph{personalized page rank} \cite{personalized_page_rank} using a random walk approach similar to the one implemented in Babelfy. This step is performed offline.

@@

The idea behind the PageRank \cite{pageRank} algorithm is to estimate the relevance of a website to a search query not only by whether the search terms appear on that page, but also by how many other pages were providing a hyperlink to the website in question. As DBpedia entries form a highly interconnected graph, the same principle can be applied in order to determine the page rank of a resource in DBpedia.

>>>>

We compare our approach to state-of-the-art tools such as FOX~\cite{foxdemo} and DBpedia spotlight~\cite{spotlight}, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset. Further, we show that Veasel beats state-of-the-art named entity linking approaches in terms of speed.

@@

The input data for {\acronym} is a regular piece of text, for example a newspaper article, in which entity-representing sequences of tokens (\emph{fragments}) are already identified (we use the Stanford NER~\cite{ner}). For a given fragment, the algorithm's task is to determine the matching real-world entity. It does so by picking the most likely entity from a set of entity candidates, e.g. specified in a knowledge base, in our case DBpedia.

@@

The semantic neighborhood signature for an entity is computed in a similar way as Babelfy~\cite{babelfy} does, except that instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base we use a graph of interlinked Wikipedia pages, where each page is a vertex and each link between pages is an edge. The idea is to identify for each resource all other resources it is closely related to. This is a two step process. First, the edges are assigned weights so that edges in denser parts of the graph become more important. The weight of an edge $\mathrm{weight}(v, v')$ is the number of directed triangles (directed cycles of length 3) it appears in:
$$\mathrm{weight}(v, v') := |\{(v, v', v'') : (v, v'), (v', v''), (v'', v) \in E\}| + 1$$

@@

We compute a measure similar to the \emph{personalized page rank}~\cite{personalized_page_rank} using a random walk approach similar to the one implemented in Babelfy. This step is performed offline.

@@

The idea behind the PageRank~\cite{pageRank} algorithm is to estimate the relevance of a website to a search query not only by whether the search terms appear on that page, but also by how many other pages were providing a hyperlink to the website in question. As DBpedia entries form a highly interconnected graph, the same principle can be applied in order to determine the page rank of a resource in DBpedia.
